\begin{thebibliography}{150}

    % Set Reference ID carefully, do not use replication
    
   \bibitem {1}P. Burt, E. Adelson, The laplacian pyramid as a compact image code, IEEE Trans.Commun. 31 (4) (1983) 532–540..
 
 \bibitem {2} P. Burt, E. Adelson, The laplacian pyramid as a compact image code, IEEE Trans.Commun. 31 (4) (1983) 532–540
 

\bibitem {3} A. Toet, Image fusion by a ratio of low pass pyramid, Pattern Recogn. Lett. 9(4)(1989) 245–253.

\bibitem {4} V. Petrovic, C. Xydeas, Gradient-based multiresolution image fusion, IEEE Trans. Image Process. 13 (2) (2004) 228–237.


\bibitem {5} H. Li, B. Manjunath, S. Mitra, Multisensor image fusion using the wavelet transform, Graph. Models Image Process. 57 (3) (1995) 235–245


\bibitem{6} M. Beaulieu, S. Foucher, L. Gagnon, Multi-spectral image resolution refinement using stationary wavelet transform, in: Proceedings of 3rd IEEE International Geoscience and Remote Sensing Symposium, 2003, pp. 4032–4034


\bibitem{7}J. Lewis, R. OCallaghan, S. Nikolov, D. Bull, N. Canagarajah, Pixel- and regionbased image fusion with complex wavelets, Inform. Fusion 8 (2) (2007) 119–130.

\bibitem{8} F. Nencini, A. Garzelli, S. Baronti, L. Alparone, Remote sensing image fusion using the curvelet transform, Inform. Fusion 8 (2) (2007) 143–156

\bibitem{9}M. Aharon, M. Elad, and A. Bruckstein,“K-SVD: an algorithm for designing overcomplete dictionaries for sparse representation,”IEEE Trans. Signal Process.54(11), 4311–4322(2006)

\bibitem{10}T. Guha and R. K. Ward,“Learning sparse representations for human action recognition,” IEEE Trans. Pattern Anal. Mach. Intell 34(8),1576–1588 (2012)

\bibitem{11}M. S. Lewicki and T. J. Sejnowski,“Learning overcomplete representations,”Neural Comput.12(2), 337–365 (2000)

\bibitem{12}K. Engan, S. O. Aase, and J. H. Husoy,“Method of optimal directions for frame design,”in Int. Conf. Audio, Speech and Signal Processing, Vol. 5, pp. 2443–2446, IEEE Press, Phoenix, AZ (1999).

\bibitem{13} M. Yaghoobi, T. Blumensath, and M. E. Davies,“Dictionary learning for sparse approximations with the majorization method,”IEEE Trans. Signal Process.57(6), 2178–2191 (2009)

\bibitem{14} L. Landweber,“An iterative formula for fredholm integral equations of the first kind,”Am. J. Math.73(3), 615–624 (1951)

\bibitem{15}B. Yang and S. Li,“Multifocus image fusion and restoration with sparse representation,”IEEE Trans. Instrum. Meas. 59(4), 884–892 (2010).

\bibitem{16}B. A. Olshausen and D. J. Field, “Emergence of simple-cell receptive field properties by learning a sparse coding for natural images,”Nature, vol. 381, no. 6583, pp. 607–609, Jun. 1996

\bibitem{17}G. Davis, S. Mallat, and M. Avellaneda, “Adaptive greedy approximations,”Constr. Approx., vol. 13, no. 1, pp. 57–98, Mar. 1997.

\bibitem{18} M. Aharon, M. Elad, and A. Bruckstein, “K-SVD: An algorithm for designing overcomplete dictionaries for sparse representation,”IEEE Trans.Signal Process., vol. 54, no. 11, pp. 4311–4322, Nov. 2006.

\bibitem{19}I. F. Gorodnitsky and B. D. Rao, “Sparse signal reconstruction from limited data using FOCUSS: A re-weighted norm minimization algorithm,”IEEE Trans. Signal Process., vol. 45, no. 3, pp. 600–616, Mar. 1997.

\bibitem{20}M. Elad and M. Aharon, “Image denoising via sparse and redundant representations over learned dictionaries,” IEEE Trans. Image Process.,vol. 15, no. 2, pp. 3736–3745, Dec. 2006.

\bibitem{21}Iain M.Johnstone David L Donoho. Adapting to smoothness via wavelet shrinkage.Journal of the Statistical Association, 90(432):1200–1224, Dec 1995.

\bibitem{22} David L Donoho. Ideal spatial adaptation by wavelet shrinkage. Biometrika,

\bibitem{23} David L Donoho. De-noising by soft thresholding. IEEE Transactions on Information Theory, 41(3):613–627, May 1995.

\bibitem{24}S. Mallat, Z. Zhang, Matching pursuits with time-frequency dictionaries, IEEE Trans. Signal Process. 41 (12) (1993) 3397–3415.

\bibitem{25}S. Li, B. Yang, J. Hu, Performance comparison of different multi-resolution transforms for image fusion, Inform. Fusion 12 (2) (2011) 74–84.

\end{thebibliography}
